More Tests

### 2022-04-27 Manuscript/Block-Bootstrap.Rmd
Two Directories

print(root_0.2_2)
```
Observed coverage rates seem to be lower, when n was 169 and 144, coverage rates below .90 were recorded for the non-moving method.

@@

print(root_0.4_2)
```

@@

Observed coverage rates seem to be lower, when n was 144 and 121, both coverage rates recorded were below .90.

@@

print(root_0.6_2)
```
Observed coverage rates seem to be lower, when n was 529, a coverage rate below .90 was recorded for the non-moving method.

@@

Observed coverage rates seem to be lower, when n was 324 and 256, coverage rate below .90 was recorded for the non-moving methods.

@@

print(root_0.8_3)
```
Observed coverage rates seem to be lower, when n was 676, coverage rates below .90 was recorded for both methods

@@

print(root_0.8_4)
```
All of the coverage rates are below .90.

>>>>

print(root_0.2_2)
```
Observed coverage rates seem to be lower...

@@

print(root_0.4_2)
```
Coverage for n = 256 below .90.

@@

Observed coverage rates seem to be lower, when n was 144 and 121, both coverage rates recorded were below .90. For n = 225, coverage rate below .90 recorded for moving method.

@@

print(root_0.6_2)
```

@@

Observed coverage rates seem to be lower, when n was 324 and 256, coverage rate below .90 was recorded for the moving methods.

@@

print(root_0.8_3)
```
Observed coverage rates seem to be lower, when n was 841 and 784, coverage rates below .90 were recorded for non-moving method, and when n was 900, coverage rate fro moving method was below .90.

@@

print(root_0.8_4)
```
All but 3 of the coverage rates are below .90.
